\thesistitle

### 2019-08-18 sections/related_work.tex
Aries

\subsection{Aries}
A tool named Aries~\cite{higo2004aries, higo2008metric} focuses on the detection of refactorable clones. They do this based on the relation between clone instances through inheritance, similar to Fontana et al.~\cite{fontana2012duplicated}. This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.

We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, all of these tools only support a subset of all harmful clones that are found. Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable. Finally, all published approaches have limitations, such as false positives in their clone detection~\cite{chen2018clone} or being limited to clone pairs~\cite{higo2008metric}.

>>>>

\subsection{Aries}
A study by Higo et al.~\cite{higo2004aries, higo2008metric} looks into to what extent clones can be refactored. They show code examples and to what entent they can be cloned. For instance, they look into what parts of a clone can be extracted to a new method. They define that partially cloned blocks obstruct method extraction. They propose t make the clone smaller to find a part of the clone that can be refactored. This is similar to our ``partial block'' category of Section~\ref{sec:refactorabilitysetup} and our discussion in Section~\ref{sec:partialblockdiscussion}.

Higo et al. also look into the amount of variability that can be allowed between clone fragments. Figure~\ref{fig:higomerge} shows an example of merging two code fragments from this study. In this figure, the clone spans a part of a different block so it cannot be refactored. However, they propose to ommit both ``else if'' lines from the merged fragment so that it can be refactored (in our study we would have flagged these clones as ``partial block'' and thus unsuitable for refactoring). They also allow variability in literals and variables and replace them with method parameters.

\begin{figure}[H]
  \includegraphics[width=1\textwidth]{img/higo}
  \caption{Example of merging two code fragments from Higo et al.~\cite{higo2008metric}.}
  \label{fig:higomerge}
\end{figure}

Higo et al. propose a tool named Aries~\cite{higo2004aries, higo2008metric} that focuses on the detection of refactorable clones. They focus entirely on whether a clone \textbf{can} be refactored and not whether it \textbf{should} be refactored. This tool only proposes a refactoring opportunity and does not provide help in the process of applying the refactoring.

\subsection{Coming up :)}
We investigated several research efforts that look into code clone refactoring~\cite{alwaqfi2017refactoring, chen2018clone, koni2001scenario}. However, all of these tools only support a subset of all harmful clones that are found. Also, these tools are limited to suggesting refactoring opportunities, rather than actually applying refactorings where suitable. Finally, all published approaches have limitations, such as false positives in their clone detection~\cite{chen2018clone} or being limited to clone pairs~\cite{higo2008metric}.
